An analysis of financial globalization: excess saving in East Asia and Pacific region and its effect in US interest rate

### 2024-04-19 paper/paper.qmd
typo fixing

---
title: "An analysis of financial globalization: excess saving in East Asian and its effect in US interest rate"
author: Yingzhi Zhang
thanks: "Code and data are available at: https://github.com/melissazhangyz/financial_globalization."
date: today
date-format: long
abstract: "The United States has witnessed its interest rate with secular deline. While the influencing factors for interest rate are various, a focus on global excess saving has driven the discussion to the global financial market. Data suggests that, instead of US itself, insdutrializing countries in East Asia and Pacific (EAP) area are major contributor to the global saving glut. In this study, a multiple linear regressio model is tested using 40-years data to examine the correlation between US interest rate and gross saving rate in EAP. The statistical result suggests that as EAP countries increase there saving rate, US interest rate tend to decrease in a significant degree. "
format: pdf
header-includes: 
- \usepackage{float}
- \usepackage{amsmath}
mainfont: Times New Roman
sansfont: Times New Roman
number-sections: true
bibliography: references.bib
toc: true
toc-depth: 3
---

>>>>

---
title: "An analysis of financial globalization: excess saving in East Asia and Pacific region and its effect in US interest rate"
author: Yingzhi Zhang
thanks: "Code and data are available at: https://github.com/melissazhangyz/financial_globalization."
date: today
date-format: long
abstract: "The United States has witnessed its interest rate with secular deline. While the influencing factors for interest rate are various, a focus on global excess saving has driven the discussion to the global financial market. Data suggests that, instead of US itself, insdutrializing countries in East Asia and Pacific (EAP) area are major contributor to the global saving glut. In this study, a multiple linear regressio model is tested using 40-years data to examine the correlation between US interest rate and gross saving rate in EAP. The statistical result suggests that as EAP countries increase there saving rate, US interest rate tend to decrease in a significant degree. "
format: pdf
header-includes: 
- \usepackage{float}
- \usepackage{amsmath}
mainfont: Times New Roman
sansfont: Times New Roman
number-sections: true
bibliography: references.bib
toc: true
toc-depth: 3
---
